### 2022-04-08 GB_Simulation_3Species.Rmd
final movement and matrix normalization

@@

#decreasing population settings
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 2, "b" = 4, "cv" = 0),
                                       "spp2" = c("model" = "BH", "a" = 2, "b" = 4, "cv" = 0),
                                       "spp3" = c("model" = "BH", "a" = 2, "b" = 4, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), #CORRECT FOR YTF
                     M = c("spp1" = 0.25+0, "spp2" = 0.35+0, "spp3" = 0.2+.05), #CHANGE
                     K = c("spp1" = 0.3, "spp2" = 0.3, "spp3" = 0.3), #CHANGE
                     nz = nonzero_idx)

>>>>

```{r}
library(Rcpp)

#just sum matrix for denominator and then do x1 / sum_mat. 1 year took 4.059 minutes
cppFunction('

            double sum_mat(NumericVector M){

            double S = sum(M);

            return S;
            }
            ')

sum(hab$hab$spp1[nonzero_idx[[1]]])

sum_mat(hab$hab$spp1[nonzero_idx[[1]]])

#normalize entire matrix in C++. 4.95 minutes for 1 year.
#I think because I must use as.matrix to entier MM. Will change to vector instead below

cppFunction('

NumericMatrix norm_mat(NumericMatrix M, NumericMatrix MM, NumericMatrix Nzero_vals) {
  //NumericMatrix MM = M(! is_na(M));
  double sm = sum(MM);
  int nNonzero = Nzero_vals.nrow();

  int nrow = M.nrow();
  int ncol = M.ncol();

  NumericMatrix new_val(nrow, ncol);// for storing new values

  for(int p = 0; p < nNonzero; p++)  {

    new_val(Nzero_vals(p,0)-1,Nzero_vals(p,1)-1) = M(Nzero_vals(p,0)-1,Nzero_vals(p,1)-1) / sm ;

  return new_val;
}
')

#normalize entire matrix in C++. Send MM as vector instead of using as.matrix()
#took 4.71 minutes to run 1 year
#norm_mat(x1, x1[nz[[s]]],Nzero_vals = nz[[s]])
cppFunction('

NumericMatrix norm_mat(NumericMatrix M, NumericVector MM, NumericMatrix Nzero_vals) {

  double sm = sum(MM);
  int nNonzero = Nzero_vals.nrow();

  int nrow = M.nrow();
  int ncol = M.ncol();

  NumericMatrix new_val(nrow, ncol);// for storing new values

  for(int p = 0; p < nNonzero; p++)  {

    new_val(Nzero_vals(p,0)-1,Nzero_vals(p,1)-1) = M(Nzero_vals(p,0)-1,Nzero_vals(p,1)-1) / sm ;

  return new_val;
}
')

#integrated the normalization into the movement command. This runs the fastest: 3.82 minutes for 1 year

@@

profvis::profvis({
#decreasing population settings
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 2, "b" = 4, "cv" = 0),
                                       "spp2" = c("model" = "BH", "a" = 2, "b" = 4, "cv" = 0),
                                       "spp3" = c("model" = "BH", "a" = 2, "b" = 4, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), #CORRECT FOR YTF
                     M = c("spp1" = 0.25+0, "spp2" = 0.35+0, "spp3" = 0.2+.05), #CHANGE
                     K = c("spp1" = 0.3, "spp2" = 0.3, "spp3" = 0.3), #CHANGE
                     nz = nonzero_idx)
